The Units of Permissionless Consensus: \\ Towards Mobile and Edge Computing

### 2022-11-19 theoretical-consensus/article/article.tex
change figures placement
fix genesis block & readme

This paper presents an overview of the consensus problem
applicable to permissionless environments. Starting from 
the classical roots of consensus in distributed systems,
transitioning to the more recent developments in the
field of permissionless consensus, this paper also reviews
the common approaches and architectural design of the most well known protocols, 
and discusses the trade-offs between the different approaches.
Finally, this paper points out the challenges that
permissionless consensus faces in the context of resource
constrained environments, such as mobile and edge computing.
It identifies and argues about the current approaches to address these challenges,
and shows potential research directions.

@@

@@

The remaining piece of the puzzle is the device discovery issue. The way the internet works does not
allow for direct device pairing and easy peer discovery. The modern web generally follows a 
client-server model with the centralization of resources. And, for this project, there was the need
for a mechanism that would allow the peers to connect to each other to then proceed to synchronize
the information. The \emph{GUN} ecosystem established a commonly accepted solution for this issue, that, 
very shortly, depends on setting up \emph{relay} peers that have somewhat static addresses and that can 
serve as reference points and pairing gateways for the nodes to discover and establish direct communications 
with their peers. For development and demonstration purposes, multiple relay nodes were set up, running 
as \emph{Docker} containers, with static ports and addresses, that could then be referenced in the web 
page generation, for the other mobile and dynamic peers to connect to and make contacts with the rest of the network.
The communication fashion is abstracted by the libraries used, but, generally, it happens either via \emph{WebSockets}
or \emph{WebRTC} technology. Figure \ref{fig:in-browser-pow-topology} shows the topology of the whole system.

>>>>

This paper presents an overview of the consensus problem
applicable to permissionless environments. Starting from 
the classical roots of consensus in distributed systems,
transitioning to the more recent developments in the
field of permissionless consensus, this paper also reviews
the common approaches and architectural design of the most well known protocols, 
and discusses the trade-offs between the different strategies.
Finally, this paper points out the challenges that
permissionless consensus faces in the context of resource
constrained environments, such as mobile and edge computing.
It identifies and argues about the current approaches to address these challenges,
and shows potential research directions.

@@

The remaining piece of the puzzle is the device discovery issue. The way the internet works does not
allow for direct device pairing and easy peer discovery. The modern web generally follows a 
client-server model with the centralization of resources. And, for this project, there was the need
for a mechanism that would allow the peers to connect to each other to then proceed to synchronize
the information. The \emph{GUN} ecosystem established a commonly accepted solution for this issue, that, 
very shortly, depends on setting up \emph{relay} peers that have somewhat static addresses and that can 
serve as reference points and pairing gateways for the nodes to discover and establish direct communications 
with their peers. For development and demonstration purposes, multiple relay nodes were set up, running 
as \emph{Docker} containers, with static ports and addresses, that could then be referenced in the web 
page generation, for the other mobile and dynamic peers to connect to and make contacts with the rest of the network.
The communication fashion is abstracted by the libraries used, but, generally, it happens either via \emph{WebSockets}
or \emph{WebRTC} technology. Fig. \ref{fig:in-browser-pow-topology} shows the topology of the whole system.

@@
